Comparison of dimensionality reduction schemes for derivative-free global optimization algorithms

### 2018-07-11 2018/YSC/ysc_paper.tex
YSC: fix typo
YSC: add information about grant

\address[a]{Lobachevsky State University of Nizhni Novgorod, 23 Prospekt Gagarina (Gagarin Avenue), 603950 Nizhnij Novgorod, Russia}

@@

\end{keyword}
\cortext[cor1]{Corresponding author. E-mail address: sovrasov.vlad@gmail.com}
\end{frontmatter}

@@

%------------------------------------------------------------------------------

>>>>

\address[a]{Lobachevsky State University of Nizhni Novgorod, 23 Prospekt Gagarina (Gagarin Avenue), 603950 Nizhni Novgorod, Russia}

@@

\end{keyword}
\cortext[cor1]{Corresponding author.}
\end{frontmatter}

@@

\section*{Acknowledgements}

The study was supported by the Russian Science Foundation, project No 16-11-10150.
%------------------------------------------------------------------------------
